The problem and promise of scale in multilayer networks

### 2020-01-22 paper/manuscript.Rmd
describe habitat types

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division. Available landcover classification included nine habitat types, which we distilled into two broad categories: open and closed habitat types. Open habitat consisted of lichen, wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.

@@

Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer)

#### Generating multilayer social networks

1. landcover scale

>>>>

### Landscape data and habitat classification
Landscape classification data were provided by the Newfoundland and Labrador Wildlife Division. Available landcover classification included nine habitat types at 30x30m resolution. We distilled the landcover types into three broad categories: foraging habitat, open habitat, and closed habitat. Foraging habitat consisted of lichen habitat, open habitat consisted of wetland, rocky barrens, frozen lakes, and anthropogenic habitat types, while closed habitat consisted of coniferous forest, conifer scrub, broadleaf forest, and mixed-wood forest habitat types.

@@

Our multilayer social network therefore consisted of social association networks generated in two habitat types (open and closed) and in two seasons (winter and summer).

#### Landcover scale
